Conjure: Summoning Proxies from Unused Address Space

### 2019-09-02 paper/paper.tex
Pass on Abstract, Introduction, and Conclusion.

We present \scheme, an improved Refraction Networking approach
that overcomes these limitations by leveraging unused address space at
deploying ISPs. Instead of using real websites as the decoy destinations
for proxy connections, our scheme creates seemingly legitimate hosts
on demand, at IP addresses where no web server exists.
These phantom hosts are difficult for a censor to distinguish from
real ones, but can be used by clients as proxies.  We define the
\scheme protocol, analyze its security, and evaluate a
prototype using an ISP testbed.
Our results suggest that \scheme can be harder to block
than TapDance, is simpler to maintain and deploy,
and offers substantially better network performance.

@@

\TODO{Phantom hosts are cheap to create, allowing for discardable or even one-time-use
proxy servers}. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
%TODO: don't need to hedge on IPv4 anymore..? could cut
\scheme supports both IPv4 and IPv6,
though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

\scheme provides a much larger degree of engineering flexibility than previous
Refraction Networking schemes. Due to its modular design, different registration
protocols and applications can be used. One obvious direction is to further
study such alternatives. For instance, while we use a TapDance-like
covert channel for registration, we could potentially cut down on the overhead of one-time
registration by using port-knocking or using a Telex-style~\cite{telex11} tag (in the Client Hello rather than Application Data).

\paragraph{Client-side applications}
\TODO{On the application side}, \scheme provides an interesting opportunity to explore
\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.,
a mask site), our application could connect back to a client after registration
from the phantom host address. Possible protocols could include WebRTC, mentioned in
Section~\ref{sec:webrtc}, or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.

\paragraph{Traffic analysis}
\scheme could also support applications that tradeoff performance for
observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
cost of overhead. \scheme applications could implement Slitheen
in order to perfectly mimic the mask site's latency, packet timings, and payload
sizes. In addition, careful choice of mask sites may allow for higher
performance, as sites with more replaceable content can carry more covert data.

@@

%\section{Conclusion}
%.25 page

%\TODO{Write (0.25 page}

>>>>

We present \scheme, an improved Refraction Networking approach
that overcomes these limitations by leveraging unused address space at
deploying ISPs. Instead of using real websites as the decoy destinations
for proxy connections, our scheme connects to IP addresses where no 
web server exists leveraging proxy functionality from the core of the network.
These phantom hosts are difficult for a censor to distinguish from
real ones, but can be used by clients as proxies.  We define the
\scheme protocol, analyze its security, and evaluate a
prototype using an ISP testbed.
Our results suggest that \scheme can be harder to block
than TapDance, is simpler to maintain and deploy,
and offers substantially better network performance.

@@

Phantom hosts are cheap to connect to, and greatly expand the 
number of viable proxy endpoints that a censor must consider. This increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
could theoretically detect 90\% of phantom hosts with confidence does not significantly reduce the
effectiveness of a circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.

\scheme supports both IPv4 and IPv6,
though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the proxy transport, connections can live as
long as needed, without the complexity faced by TapDance.

@@

\scheme provides a much larger degree of engineering flexibility than previous
Refraction Networking schemes. Due to its modular design, different registration
protocols and proxy transports can be used interchangeably by the client. The
flexibility of proxy transports and simplicity of registration allows \scheme to
incorporate state of the art censorship circumvention tools and resist 
nation-state censors.

One obvious future direction is to study new options for registration and proxy transport. For instance, while 
\scheme currently uses a refraction networking covert channel for registration, we could potentially 
cut down on the overhead of one-time registration by using port-knocking or using a 
Telex-style~\cite{telex11} tag (in the Client Hello rather than Application Data).

\paragraph{Client-side applications}
\scheme provides an interesting opportunity to explore
\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.,
a mask site), our transport itself could connect to a newly registered client
from the phantom host address. Possible protocols could include WebRTC, mentioned in
Section~\ref{sec:webrtc}, or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.

\paragraph{Traffic analysis}
\scheme could also support applications that tradeoff performance for
observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
cost of overhead. \scheme transports such as mask site could implement Slitheen
in order to perfectly mimic the decoy site's latency, packet timings, and payload
sizes. In addition, careful choice of mask sites may allow for higher
performance, as sites with more replaceable content can carry more covert data.

@@
